### 2017-10-10 manuscript.rmd
reexecuted pdf
simplified dependencies

---
bibliography: manuscript.bib
csl: systematic-biology.csl
output:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
---

@@

	# Biological
#	library( edgeR )
	library( treeio )
	library( hutan )	# https://github.com/caseywdunn/hutan
	library( ape )
#	library( agalmar )	# https://github.com/caseywdunn/agalmar
	library( picante )  # cor.table
	library( phytools ) # phylosig
  library( vegan )
  library( ggtree )
  library( phangorn )
  library( geiger )
  library( phylobase )
  library( adephylo )
  library( geomorph ) #physig
  library( phylolm )

>>>>

---
bibliography: manuscript.bib
csl: systematic-biology.csl
output:
  pdf_document:
    fig_caption: yes
---

@@

	# Biological
	library( treeio )
	library( hutan )	# https://github.com/caseywdunn/hutan
	library( ape )
	library( picante )  # cor.table
	library( phytools ) # phylosig
  library( vegan )
  library( ggtree )
  library( phangorn )
  library( geiger )
  library( phylobase )
  library( adephylo )
  library( geomorph ) #physig
  library( phylolm )
